Supplementary Materials

### 2019-01-22 sup_mat/sup_mat.Rmd
Added exclusion criteria
Added in accuracy exclusion criteria for ACS task

# what data do we need?
# get line seg acc and rt 
ls_acc_RT <- readRDS(file = "../../Scripts/lineseg/scratch/processedRTandAccData.Rda")

@@

```{r processing ls data, echo = FALSE, include = FALSE}
# load in unprocessed data 
load("../../Scripts/lineseg/scratch/unfiltered_fixDat")
load("../../Scripts/lineseg/scratch/unfiltered_trlDat")
trlDat_unf <- trlDat
# tidy 
rm(trlDat)

@@

# get removed fixations data 
load("../../Scripts/lineseg/scratch/processedFixationData")
# get difference value 
num_removed <- num_fixations - nrow(fixDat)

@@

# Get accuracy for each participant 
# probably want to exclude participant 39 going by their accuracy 
plt_ACS_mean_acc <- dat_ACS %>%
  filter(Block_num > 0) %>%
  mutate(sdev = sd(RT)) %>%
  filter(RT > RT - 3*sdev,
         RT < RT + 3*sdev,
         RT > 300) %>%
  group_by(SubNo) %>%
  summarise(mean_acc = mean(Acc)) %>%
  mutate(mean_acc_ov = mean(mean_acc)) %>%
  ggplot(aes(SubNo, mean_acc)) + 
  geom_point() + 
  theme_bw()
plt_ACS_mean_acc$labels$x <- "Participant"
plt_ACS_mean_acc$labels$y <- "Mean Accuracy"
# plt3

>>>>

# what data do we need?
# get line seg acc and rt 
ls_acc_RT <- readRDS(file = "../Scripts/lineseg/scratch/processedRTandAccData.Rda")

@@

```{r processing ls data, echo = FALSE, include = FALSE}
# load in unprocessed data 
load("../Scripts/lineseg/scratch/unfiltered_fixDat")
load("../Scripts/lineseg/scratch/unfiltered_trlDat")
trlDat_unf <- trlDat
# tidy 
rm(trlDat)

@@

# get removed fixations data 
load("../Scripts/lineseg/scratch/processedFixationData")
# get difference value 
num_removed <- num_fixations - nrow(fixDat)

@@

# Get accuracy for each participant 
# probably want to exclude participant 39 going by their accuracy 
plt_ACS_mean_acc <- dat_ACS %>%
  filter(Block_num > 0) %>%
  mutate(sdev = sd(RT)) %>%
  filter(RT > RT - 3*sdev,
         RT < RT + 3*sdev,
         RT > 300) %>%
  ungroup() %>%
  mutate(mean_acc_ov = mean(Acc)) %>%
  group_by(SubNo) %>%
  summarise(mean_acc = mean(Acc),
            mean_acc_ov = mean(mean_acc_ov)) %>%
  mutate(sd_acc = sd(mean_acc)) %>%
  filter(mean_acc > mean_acc_ov - 3*sd_acc) %>%
  ggplot(aes(SubNo, mean_acc)) + 
  geom_point() + 
  theme_bw()
plt_ACS_mean_acc$labels$x <- "Participant"
plt_ACS_mean_acc$labels$y <- "Mean Accuracy"
# plt3
